Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Open problems: review

\begin{quote}
    TBD: state that ``A library for reusable pieces of specification would be
    useful.''
\begin{itemize}
    \item
        In Section~\ref{sec:reusable-specs}, we showed how to reuse
        pieces of specification.
    \item
        We think a library of reuseable specs would be a good idea
    \item
        It would be possible and useful to write a library that
        provides reusable pieces of specification, for many of
        Haskell's standard classes.
        (similar in purpose to
        {\tt
        checkers}\footnote{http://hackage.haskell.org/package/checkers})
      \item copied here from Section~\ref{sec:reuseable-pecs}:

        Reusable spec is an idea to scrap boilerplate of evidence.
        For instance, without reusable spec,
        each developer of an instance of a type class should
        express evidence for its laws.
        Since instances of a type class share API,
        we can avoid such boilerplate.
        The following is an example to implement
        evidence for Monoid laws:

        We should ensure the practicality of reusable spec and
        prepare reusable spec to cover variety of type classes.

\end{itemize}
\end{quote}

When Hspec finds evidence that does not hold, it reports the
corresponding behavior to the developer.  It would be useful to
include the source file and location where the failing evidence is
defined, so that the developer can find it immediately.
Extending GHC with a mechanism similar to JHC's
\verb|SRCLOC_ANNOTATE| pragma\footnote{%
http://repetae.net/computer/jhc/jhc.shtml} would allow to solve this.

\begin{quote}
    sol: should we just remove the next paragraph?
\end{quote}

Feedback for failing QuickCheck properties is not always as useful as
it could be.
Combinators, similar to {\tt shouldBe}, that construct QuickCheck {\tt
Result}s could improve the situation.

Cucumber~\cite{cucumber} is a higher-level approach to BDD for Ruby, and
it is typically used in combination with RSpec.
It focuses on user stories, to assist the developer in delivering
value to the stakeholder.
There is nothing comparable to Cucumber for Haskell, yet.  And we think
it would be interesting to explore, whether it is possible to apply
Cucumber's approach to BDD to Haskell.

>>>>

In Section~\ref{sec:reusable-specs}, we showed how to reuse pieces of
specification.  It would be possible and useful to write a library
that provides reusable pieces of specification, for many of Haskell's
standard classes (similar in purpose to {\tt
checkers}\footnote{http://hackage.haskell.org/package/checkers}).
This would provide a convenient mechanism for developers to document
and test that their instance definitions are well-behaved.

When Hspec finds failing evidence, it reports the corresponding
behavior to the developer.  It would be useful to include source
locations for failing evidence, so that the programmer can find the
corresponding spec immediately. Solving this with GHC requires
Template Haskell.  Extending GHC with a mechanism
similar to JHC's \verb|SRCLOC_ANNOTATE| pragma\footnote{%
http://repetae.net/computer/jhc/jhc.shtml} would allow to solve this
without Template Haskell.

Cucumber~\cite{cucumber} is a higher-level approach to BDD for Ruby, and
it is typically used in combination with RSpec.
It focuses on user stories, to assist the developer in delivering
value to the stakeholder.
There is nothing comparable to Cucumber for Haskell, yet.  And we think
it would be interesting to explore, whether it is possible to apply
Cucumber's approach to Haskell.
